Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-26 paper.tex
adopted jasper's comment to Sec3
final version to IRC first round

Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles.
In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with a harder fragmentation are present.
The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
These correlations also persist in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
The results are compared to $\pythiashoving$, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  
$\pythiashoving$ model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of  $p_{\mathrm T}$ dependence both for the unbiased and jet events.
The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

>>>>

Long-range azimuthal correlations are measured in high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles.
In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with a harder fragmentation are present.
The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
These correlations also persist in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
The results are compared to $\pythiashoving$ calculations.  
$\pythiashoving$ model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of $p_{\mathrm T}$ dependence both for the unbiased and jet events.
The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-06-26 sec_ana.tex
final version to IRC first round

%LHC at CERN produces various interesting phenomena including the ridge effect that is the main topic of the document in pp collisions with the highest center-of-mass energy in the world.
%Recent center-of-mass energy in pp collisions reaches up to $\sqrt{s} = 13$~TeV during the last LHC Run 2 period. 
The analysis is based on the data sets in pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 in the LHC Run 2 period. The full description of ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}. The present analysis mainly utilizes V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.

@@

%The multiplicity class is classified by the signal amplitude of the V0 detector.
The high multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE. Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events~\cite{}. Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.

@@

The ridge yield is further studied by exploiting the largest momentum transfer between the initial partons in a given event, which results from the hard scattering. In this article, larger momentum transfer denotes harder event scale. The larger momentum transfer is also expected to be connected with the shorter impact parameters in pp collisions in average~\cite{Sjostrand:1986ep,Frankfurt:2010ea} so that the event scale can be indirectly connected with the impact parameters.
% The ridge yield is further studied by exploiting the momentum transfer between the interacting partons,so called, event scale.  On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
The event scales are set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since hard scattering produces leading tracks with a high $p_\mathrm{T}$ or jets. The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle. Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$. Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle. The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured for the $k_{\rm{T}}$ algorithm with $R = 0.2$.

@@

\section{Systematic Uncertainty}
\label{sec:uncertainties}
The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction. Each source is assumed to be uncorrelated. The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection. The uncertainty from the track selection is estimated by changing the selection criteria. The uncertainty from the yield extraction procedures can be categorized into long-range definition and ZYAM procedure. The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction.
%Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. 
Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlation function constructed by generated particles from the event generator.
The uncertainty of $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$ is summarized by averaging each uncertainty for given $\pttrig$ and $\ptassoc$. The uncertainty of $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$ is summarized by averaging the each uncertainty for a given $\ptlead$ and $\ptjet$ selection, respectively.
\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty (\%)} \\\cline{2-4}
         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
Pileup cut			& $\sim$0.8	&0--4		&0--4		\\ \hline
Primary Vertex		& $\sim$2.4	&1--12	&1-8		\\ \hline

@@

M.C. non-closure*	& $\sim$2.5 	&1		&1		\\ \hline
Total 			& $\sim$9.7	&4--16	&4--22	\\ 
\hline 
\end{tabular}
\label{tab:syst}
\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
\end{table}

>>>>

%LHC at CERN produces various interesting phenomena including the ridge effect that is the main topic of the document in pp collisions with the highest center-of-mass energy in the world.
%Recent center-of-mass energy in pp collisions reaches up to $\sqrt{s} = 13$~TeV during the last LHC Run 2 period. 
The analysis is based on the data sets in pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 in the LHC Run 2 period. The full description of ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}. The present analysis mainly utilizes the V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.

@@

%The multiplicity class is classified by the signal amplitude of the V0 detector.
The high multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE. Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events. Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.

@@

The ridge yield is further studied by exploiting the largest momentum transfer among the initial partons in a given event, which results from the hard scattering. In this article, larger momentum transfer denotes harder event scale. The larger momentum transfer is also expected to be connected with the shorter impact parameters in pp collisions in average~\cite{Sjostrand:1986ep,Frankfurt:2010ea} so that the event scale can be indirectly connected with the impact parameters.
% The ridge yield is further studied by exploiting the momentum transfer between the interacting partons,so called, event scale.  On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
The event scales are set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since hard scattering produces leading tracks with a high $p_\mathrm{T}$ or jets. The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle. Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$. Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle. The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured for the $k_{\rm{T}}$ algorithm with $R = 0.2$.

@@

\section{Systematic Uncertainty}
\label{sec:uncertainties}
The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction. Each source is assumed to be uncorrelated. The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection. The uncertainty from the track selection is estimated by changing the selection criteria. The uncertainty from the yield extraction procedures can be categorized into long-range definition and ZYAM procedure. The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction.
%Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. 
Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlation function constructed by generated particles from the event generator.
The uncertainty of $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$ is summarized by averaging each uncertainty for given $\pttrig$ and $\ptassoc$. The uncertainty of $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$ is summarized by averaging the each uncertainty for a given $\ptlead$ and $\ptjet$ selection, respectively.
\begin{table}[h!]
\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty (\%)} \\\cline{2-4}
         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
Pileup rejection		& $\sim$0.8	&0--4		&0--4		\\ \hline
Primary Vertex		& $\sim$2.4	&1--12	&1-8		\\ \hline

@@

M.C. non-closure*	& $\sim$2.5 	&1		&1		\\ \hline
Total 			& $\sim$9.7	&4--16	&4--22	\\ 
\hline 
\end{tabular}
\label{tab:syst}
\end{table}

### 2020-06-26 sec_results.tex
final version to IRC first round

 %The associated yield per trigger particle is compared with the CMS results.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0-0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
	\label{fig:PlotDeltaPhi}
\end{figure}

Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high multiplicity class (0--0.1\%). The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of signal in the minimum bias class. The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class. The measurements in the high multiplicity class are compared with the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}. The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties. The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances. The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity. The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$. However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range. $\pythiam$ does not show any peaks in the near-side as expected and slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, which mainly come from the back to back jet correlations.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.90\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared with the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box. The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line). }
	\label{fig:PlotYSpect}
\end{figure}

The ridge yields as a function of  the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}. The particle multiplicity in this analysis is estimated with the forward subsystem (V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$. By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%. Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other. The spectrum is also compared with model calculations. $\pythiam$ gives zero yields since it does not contain the ridge effect. $\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the data as $\pttrigassoc$ increases.

@@

The ridge yield is also studied with respect to two different event scales of the hard processes. Event-scale measurement by the largest $\pt$ of particles in each event that is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$. As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high multiplicity pp collisions with $\ptlead>9$ (left) or $\ptjet>10$~GeV/$c$ (right) .  %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
It is worth noting that the correlation function with the minimum $\ptjet$ selection has double peaks along the $\Delta\eta$ axis at $\Delta\varphi = \pi$ due to the limited jet acceptance by requiring a minimum $\ptjet$.

@@

Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper). The near-side yield increases as the threshold of $\ptjet$ increases compared to one in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$. The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum. In contrast, soft jets are favored for reconstructed jets. The results are compared to
$\pythiashoving$ and $\pythiam$ calculations. $\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event scale selections. On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections. Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared with measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
	\label{fig:RidgeYield_ESE}
\end{figure}

Finally, the ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{Lead}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}. The ridge yield increases with increasing $\it{p}^{\rm{Lead}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$. $\pythiashoving$ underestimates the ridge yield with the increasing $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$, still holding presence of the ridge. $\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0--0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to $\pythiashoving$ and orange line corresponds to $\pythiam$}
	\label{fig:PlotDeltaPhi}
\end{figure}

Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high multiplicity class (0--0.1\%). The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of signal in the minimum bias class. The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class. The measurements in the high multiplicity class are compared to the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}. The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties. The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances. The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity. The high multiplicity class for each model is determined by requiring the minimum number of charged particles are larger than 105, which is corresponding to the top 0--0.1\% multiplicity class based on $\pythiam$. The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$. However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range. $\pythiam$ does not show any peaks in the near-side as expected and slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, which mainly come from the back to back jet correlations.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared to the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box. The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line). }
	\label{fig:PlotYSpect}
\end{figure}

The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}. The particle multiplicity in this analysis is estimated with the forward subsystem (V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$. By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%. Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other. The spectrum is also compared with model calculations. $\pythiam$ gives zero yields since it does not contain the ridge effect. $\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the experimental measurement as $\pttrigassoc$ increases.

@@

The ridge yield is further studied with respect to two different event scales of the hard processes. Event-scale measurement by the largest $\pt$ of particles in each event that is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$. As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high multiplicity pp collisions with $\ptlead>9$ (left) or $\ptjet>10$~GeV/$c$ (right) .  %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
It is worth noting that the correlation function with the minimum $\ptjet$ selection has double peaks along the $\Delta\eta$ axis at $\Delta\varphi = \pi$ due to the limited jet acceptance by requiring a minimum $\ptjet$.

@@

Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper). Even with the event scale selection, the ridge is still visible in near-side. The near-side yield increases as the threshold of $\ptjet$ increases compared to one in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$. The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum. In contrast, soft jets are favored for reconstructed jets. The results are compared with $\pythiashoving$ and $\pythiam$ calculations. $\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event scale selections. On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections. Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared to measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
	\label{fig:RidgeYield_ESE}
\end{figure}

Finally, the ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}. The ridge yields are increased for $\it{p}^{\rm{LP}}_{\rm{T,min}} >$ 7 and $\it{p}^{\rm{Jet}}_{\rm{T,min}} \ge$ 10~GeV/$c$ compared to one from the unbiased events. A moderate increase of the ridge yields toward higher $\ptlead$ or $\ptjet$ is observed and there is no difference between two event selections within the uncertainties.
The results are compared with $\pythiashoving$ and $\pythiam$. $\pythiashoving$ doesn't show a clear $\it{p}^{\rm{LP}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$ dependence within the errors and underestimates the yields especially for the jet tagged events. $\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.
The origin of the enhanced ridge yields for higher momentum jet tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.

### 2020-06-26 sec_summary.tex
final version to IRC first round

\section{Conclusions}
\label{sec:summary}
Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV . These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class. 
The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
%In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
$\pythiashoving$ describes the yield qualitatively but its yield gets decreased more rapidly than the data as $\pttrigassoc$ increases.
Furthermore the ridge yields are studied in events, where jets with a harder fragmentation is preferred by requiring the minimum value of  the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$. The ridge structure still persist with both selections. The ridge yields increase as $\ptlead$ and $\ptjet$ increase, respectively. The latter, however, is significant than the former selection. The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

>>>>

\section{Conclusions}
\label{sec:summary}
Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV. These results are obtained in a relative pseudorapidity range $1.6 < |\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles. 
The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
%In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
$\pythiashoving$ describes the yield qualitatively but its yield is decreased more rapidly than the data as $\pttrigassoc$ increases. On the other hand, $\pythiam$ does not describe ridge in the long-range as expected. The results from $\pythiam$ also assure that the measured ridge yield is not contaminated by non-flow effects.
Furthermore the ridge yields are studied in events, where jets with a harder fragmentation is preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$. The ridge structure still persist with both selections. The ridge yields increase as $\ptlead$ and $\ptjet$ increase. The latter, however, is more significant than the former selection. The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
The results might open new way of studying impact parameter dependence of the small systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
